### 2023-08-31 sections/3-datasets.tex
getting there

Astronomers use these near-infrared spectra to achieve a better understanding of our galaxy's history.

TODO: Add details about why this dataset is a good candidate for CAKES.
TODO: Talk about distance functions used with this dataset: euclidean, cosine, Wasserstein-1d

@@

Like APOGEE, MaNGA helps astronomers understand the history of galaxies throughout their entire lifespan.

TODO: Add details about why this dataset is a good candidate for CAKES. 
TODO: Talk about distance functions used with this dataset: euclidean, cosine, Wasserstein-2d

@@

TODO: Which Silva dataset exactly are we using and what is its cardinality and dimensionality?

TODO: Add details about why this dataset is a good candidate for CAKES.
TODO: Talk about distance functions used with this dataset: hamming, levenshtein

>>>>

Astronomers use these near-infrared spectra to achieve a better understanding of our galaxy's history. This dataset 
is often used with Euclidean (L2) distance, cosine distance, and 1d-Wasserstein distance. As illustrated by Figure [TODO: ADD FIGURE NUMBER] in Section~\ref{section:methods},
this dataset is a good candidate for CAKES because it exhibits low fractal dimension.

@@

Like APOGEE, MaNGA helps astronomers understand the history of galaxies throughout their entire lifespan. This 
dataset is typically used with Euclidean (L2) distance, cosine distance, and 2d-Wasserstein distance.

TODO: Add details about why this dataset is a good candidate for CAKES.

@@

Silva 18S contains ribosomal DNA sequences of approximately 2.25 
million genomes with aligned length of 50,000 letters.

These sequences help biologists better understand the evolutionary relationships between organisms. 
This dataset is typically used with Hamming and Levenshtein distances.

TODO: Add details about why this dataset is a good candidate for CAKES.
